Verifying Demonstrations

### 2019-06-11 paper/DB-anon-cred.tex
Changes k to sk in DB-Schnorr
Changes section heading to plural form
Edits DB-Schnorr security analysis

\section{Distance-bounding \ac*{ZKPK} for discrete logarithms}%
\label{DB-anon-cred}

@@

We present the protocol in \cref{SchnorrFigure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
Further, let
\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
key~\(k\) and finally
\(\Delta t\gets \UWBPRtime\) denote the time between sending and receiving.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[k, g, q, A]\):
    \\
    \midrule

@@

    Load \(k\) into \(\UWBPR\)
    &
    & Load \(k\) into \(\UWBPR\)
    \\

@@

@@

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
This allows us to prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
the knowledge error, \(2^{-kn}\), becomes small enough.
Repeating the protocol is also needed to decrease the success probability of some of adversaries presented below.

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
  s_1\).
\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
Now, the adversary has two options.
First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
If the adversary requests \(s_b\) in full, the adversary can also guess the 
remaining \(|q|-l\) bits of \(s_{1-b}\).
Based on our assumption above, the probability of guessing these bits 
successfully is \(2^{-(|q|-l)}\).
Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
\(2^{-n}+2^{-(|q|-l)n}\).

@@

The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
Thus the probability of success is equivalent of a collision for the responses 
for the chosen challenge --- in each round.

Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}

@@

We wanted to formally verify the protocol security properties. To realize this, 
we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
originally the possibility to reason on time and space in its model.
However, thanks to a recent work by \textcite{TamarinDB}, all the common 
properties mentioned in the previous subsection can be equivalently 
characterized with a causality-based definition relying only on the order of 
messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
We are currently investigating the Tamarin interactive mode to validate as well the security properties.

>>>>

\section{Distance-bounding \aclp{ZKPK} for discrete logarithms}%
\label{DB-anon-cred}

@@

We present the protocol in \cref{SchnorrFigure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
Further, let
\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
key~\(k\) and finally
\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
and \(\UWBPRrecv\) operations.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[\sk, g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[\sk, g, q, A]\):
    \\
    \midrule

@@

    Load \(\sk\) into \(\UWBPR\)
    &
    & Load \(\sk\) into \(\UWBPR\)
    \\

@@

This protocol must be repeated \(n\) times.

@@

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for having two challenges but only one random nonce is that knowing 
the responses to both means learning \(\alpha\).
This gives us the incentives that prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from 
Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at 
\ac{DBMF} resistance.
We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
can do \iac{DBEDLC} attack to reduce the distance.
(We will solve this problem in the next section.)

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
the soundness error, \(2^{-kn}\), becomes small enough.
(Repeating the protocol is also needed to decrease the success probability of 
some of adversaries presented below.)

The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
distance-reduction through \iac{DBEDLC} attack.
Thus, any relaying will be detected.
The adversary could guess the challenge bit \(b\), request \(s_b\) from the 
prover and guess \(s_{1-b}\).
The success probability of this is \(\frac{1}{2} + \frac{1}{q}\) per round, 
thus \((\frac{q + 2}{2q})^n\) in total.

The protocol is also secure against distance hijacking due to the fact that the 
authenticating bitstring is used during the \ac{DB} phase, not the challenge 
bitstring, as is the case for the original protocol of Brands-Chaum.
Thus the probability of success is equivalent of a collision for the responses 
for the chosen challenge --- in each round.

Finally, it follows from the original Schnorr protocol that this is still 
\ac{ZK} and \iac{PK} with soundness error \(2^{-kn}\).
\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}

\subsection{Achieving \acl{DBDF} and \acl{DBTF} resistance}

\Acl{DB} protocols requires hardware implementations.
We will use a trusted hardware implementation to overcome the limitation of 
\textcite{UWBPR}, \ie that the prover and verifier be mutually trusted.
This will also require \iac{PKI} to overcome the shared-key requirement and for 
a verifier to be able verify the hardware of a prover.

@@

@@

@@

We formally verified these properties with Tamarin~\cite{meier2013tamarin}.
Thanks to recent work by \textcite{TamarinDB}, all the common properties for 
\ac{DB} protocols (except \ac{DBTF}) can be characterized with a 
causality-based definition relying only on the order of messages.
The whole Tamarin specification for our protocol is provided in 
\cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that 
we have made.
It contains a specification of the distance-bounding protocol described 
previously, a definition of the soundness and correctness properties that 
ensure the protocol actually produces the expected result, and a definition of 
the security properties we want to ensure.
